---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# timestone

<!-- badges: start -->
<!-- badges: end -->

This repository contains an `R` package to manipulate dates and times.

The main function implemented in this package is  
  - `calculate_week()`
  

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sachijay/timestone")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(timestone)
library(lubridate)

date_seq <- seq.Date(ymd("2020-01-01"),
                     ymd("2020-02-01"),
                     by = "day")

calculate_week(date_seq, "2020-01-2",
               no_of_weeks = 2, 
               as_integer = FALSE)
```


## Building the package

The following codes were used to build this package. *The prompts after each function (if shown) are handled as needed.*

```r
# Loads usethis package
library(devtools)

# Creates the package
create_package(path = here::here())

# Initialise a git repository
use_git()

# Add a file for the function
use_r(name = "calculate_week")

# Check if the package loads properly
load_all()

# Build and check the package
check()

# To add license to the package
use_mit_license("Pramoda Jayasinghe")

# Defined required packages
use_package("lubridate")
use_package("tibble")

# Create the document
document()

# To create the package readme
use_readme_rmd()

# To build the readme file
build_readme()

# Initialize testing
use_testthat()

# Formal testing the calculate_week function

```

