---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# timestone

<!-- badges: start -->
[![R build status](https://github.com/sachijay/timestone/workflows/R-CMD-check/badge.svg)](https://github.com/sachijay/timestone/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

This repository contains an `R` package to manipulate dates and times.

The main function implemented in this package is  
  - `calculate_week()`: Calculate the number of weeks past a given date
  
Visit [https://sachijay.github.io/timestone/](https://sachijay.github.io/timestone/) to view package documentation.
  

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sachijay/timestone")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example, message=FALSE}
library(timestone)
library(lubridate)

# Create a sequences of dates
date_seq <- seq.Date(ymd("2020-01-01"),
                     ymd("2020-02-01"),
                     by = "day")

# Calculate bi-weekly number of each of 
# the dates in date_seq
calculate_week(date_seq, "2020-01-2",
               no_of_weeks = 2, 
               as_integer = FALSE)
```


## Code of Conduct

Please note that the timestone project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.


## Building the package

The following codes were used to build this package. *The prompts after each function (if shown) are handled as needed.*

```r
# Loads usethis package
library(devtools)

# Creates the package
create_package(path = here::here())

# Initialise a git repository
use_git()

# Add a file for the function
use_r(name = "calculate_week")

# Check if the package loads properly
load_all()

# Build and check the package
check()

# To add license to the package
use_mit_license("Pramoda Jayasinghe")

# Defined required packages
use_package("lubridate")
use_package("tibble")

# Create the document
document()

# To create the package readme
use_readme_rmd()

# To build the readme file
build_readme()

# Initialize testing
use_testthat()

# Formal testing the calculate_week function
use_test("calculate_week_test")

# Create vignettes
use_vignette(name = "summarise_daily_data", title = "Summarise Daily Data")

# To build vignettes
build_vignettes()

# To add code of conduct
use_code_of_conduct()

# Make the package website
# install.packages("pkgdown")
use_pkgdown()
build_site()
use_github_action("pkgdown")

# Increase minor release version
use_version(which = "minor")

# Create a changelog
use_news_md()

# Add lifecycle badge
use_lifecycle_badge("Experimental")
```

