---
title: "Summarise Daily Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Summarise Daily Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To demonstrate the use of `calculate_week`, we will aggregate Covid-19 case counts in New York City (NYC) by week and month. 

First we will load the required libraries:
```{r setup, message=FALSE}
library(timestone)
library(tidyverse)
library(lubridate)
```

Covid-19 data are available through the NYC Health Department [GitHub repository](https://github.com/nychealth/coronavirus-data).

```{r, message=FALSE}
daily_cases_data <- "https://raw.githubusercontent.com/nychealth/coronavirus-data/master/trends/data-by-day.csv" %>% 
  read_csv() %>%
  select(date_of_interest, CASE_COUNT)

head(daily_cases_data)
```

Since Covid-19 reporting during the weekends, we are interested in calculating the week starting from a Wednesday. The first Wednesday after a case is reported in NYC is on 03/04/2020. Using the `calculate_week` function we can find the columns `week`, `bi-week` and `month` for each record:

```{r}
daily_data_with_wbm <- daily_cases_data %>%
  mutate(week = date_of_interest %>%
           calculate_week(start_date = "03/04/2020", 
                          date_parsing = mdy), 
         biweek = date_of_interest %>%
           calculate_week(start_date = "03/04/2020", 
                          no_of_weeks = 2, 
                          date_parsing = mdy), 
         month = date_of_interest %>%
           calculate_week(start_date = "03/04/2020", 
                          no_of_weeks = 2, 
                          date_parsing = mdy))

head(daily_data_with_wbm)
```

To visualize the summarized counts, we can use `dplyr::group_by()`:

```{r, message=FALSE}
daily_data_with_wbm %>%
  group_by(month) %>%
  summarise(count = sum(CASE_COUNT)) %>%
  filter(month != -1) %>%
  head()
```


